---
title: "Illinois_Data"
format: html
execute: 
   warning: false
---

# Loading packages
```{r}
library(readxl)
library(dplyr)
```
# 2024 data

```{r}
tt2024 <- read_xlsx("school_data/24-RC-Pub-Data-Set.xlsx", sheet = "IAR (2)")

```

# Explore data
```{r}
excel_sheets("school_data/24-RC-Pub-Data-Set.xlsx")
```

# Load 2024 test data
```{r}
illinois_test_2024 <- read_xlsx("school_data/24-RC-Pub-Data-Set.xlsx", sheet = "ELAMathScience")
```

# Load 2024 general data
```{r}
illinois_general_2024 <- suppressWarnings(read_xlsx("school_data/24-RC-Pub-Data-Set.xlsx", sheet = "General"))
```



# 2023 Data

# Explore data
```{r}
excel_sheets("school_data/23-RC-Pub-Data-Set.xlsx")
```

# Load 2023 test data
```{r}
illinois_test_2023 <- read_xlsx("school_data/23-RC-Pub-Data-Set.xlsx", sheet = "ELA Math Science")
```

# Load 2023 general data
```{r}
illinois_general_2023 <- suppressWarnings(read_xlsx("school_data/23-RC-Pub-Data-Set.xlsx", sheet = "General"))
```


# 2022 data
# Analyzing different tabs in excel sheet
```{r}
excel_sheets("school_data/2022-Report-Card-Public-Data-Set.xlsx")
```

## Loading 2022 dataset:

### Loading specfically ela, math, and science scores
```{r}
illinois_test_2022 <- read_xlsx("school_data/2022-Report-Card-Public-Data-Set.xlsx", sheet = "ELA Math Science")
```

### Loading general information about schools
```{r}
illinois_general_2022<- read_xlsx("school_data/2022-Report-Card-Public-Data-Set.xlsx", sheet = "General")
```

## Basic exploration of data:

### Found there to be 3 types of scores: for each district, school, and statewide
```{r}
unique(illinois_data_2022$Type)
```


# 2021 data
# Explore data
```{r}
excel_sheets("school_data/2021-RC-Pub-Data-Set.xlsx")
```


# Load 2021 test data
```{r}
illinois_test_2021 <- read_xlsx("school_data/2021-RC-Pub-Data-Set.xlsx", sheet = "ELA Math Science")
```

# Load 2021 general data
```{r}
illinois_general_2021 <- read_xlsx("school_data/2021-RC-Pub-Data-Set.xlsx", sheet = "General")
```


# 2020 Data

# Explore data
```{r}
excel_sheets("school_data/2020-Report-Card-Public-Data-Set.xlsx")
```


# Load 2020 test data
```{r}
illinois_test_2020 <- read_xlsx("school_data/2020-Report-Card-Public-Data-Set.xlsx", sheet = "ELA Math Science")
```

# Load 2020 general data
```{r}
illinois_general_2020 <- read_xlsx("school_data/2020-Report-Card-Public-Data-Set.xlsx", sheet = "General")
```


# 2019 Data

# Explore data
```{r}
excel_sheets("school_data/2019-Report-Card-Public-Data-Set.xlsx")
```

# Load 2019 test data
```{r}
illinois_test_2019 <- read_xlsx("school_data/2019-Report-Card-Public-Data-Set.xlsx", sheet = "ELA Math Science")
```

# Load 2019 general data
```{r}
illinois_general_2019 <- suppressWarnings(read_xlsx("school_data/2019-Report-Card-Public-Data-Set.xlsx", sheet = "General"))
```


# 2018 Data

# Explore data
```{r}
excel_sheets("school_data/Report-Card-Public-Data-Set_2018.xlsx")
```

# Load 2018 test data
```{r}
illinois_test_2018 <- read_xlsx("school_data/Report-Card-Public-Data-Set_2018.xlsx", sheet = "ELA and Math")
```

# Load 2018 general data
```{r}
illinois_general_2018 <- suppressWarnings(read_xlsx("school_data/Report-Card-Public-Data-Set_2018.xlsx", sheet = "General"))
```


# 2017 Data

# NOTE: The data from 2014-2017 is put into execel files where some rows are identified by 3 column identifiers. Thus below I rename the columns.

```{r}
illinois_test_2017 <- read_excel("school_data/2017_PARCC_SAT_ACT_enrollment.xlsx", skip = 6, col_names = FALSE)
```

```{r}
colnames(illinois_test_2017) <- c(
  "RCDTS",
  "County",
  "Dist #",
  "District Name/ School Name",
  "City",
  "ela_3_exceeding_pct",
  "math_3_exceeding_pct",
  "ela_4_exceeding_pct",
  "math_4_exceeding_pct",
  "ela_5_exceeding_pct",
  "math_5_exceeding_pct",
  "ela_6_exceeding_pct",
  "math_6_exceeding_pct",
  "ela_7_exceeding_pct",
  "math_7_exceeding_pct",
  "ela_8_exceeding_pct",
  "math_8_exceeding_pct",
  "ela_parcc_exceeding_pct",
  "math_parcc_exceeding_pct",
  "ela/math_parcc_exceeding_pct",
  "ela_sat_exceeding_pct",
  "math_sat_exceeding_pct",
  "ela/math_sat_exceeding_pct",
  "ela_PARCC/SAT/DLM_exceeding_pct",
  "math_PARCC/SAT/DLM_exceeding_pct",
  "avg_sat_11_overall",
  "avg_sat_11_ela",
  "avg_sat_11_math",
  "avg_act_overall",
  "enrollment"
)

```

# Amount of students who took the test 
```{r}
illinois_general_2017 <- read_excel("school_data/2017-Participation-Report-All-Districts.xlsx", skip = 4, col_names = FALSE)

```

```{r}
colnames(illinois_general_2017) <- c(
  "RCDTS",
  "County",
  "District/School",
  "Dist #",
  "District Name/ School Name",
  "City",
  
  "ela_participation_rate",
  "ela_met_95pct_targ4et",
  "ela_tested_enrollment",
  "ela_#_tested",
  "ela_not_tested_absent",
  "ela_not_tested_refusal",
  "ela_not_tested_scores_suppresed",
  
  "math_participation_rate",
  "math_met_95pct_target",
  "math_tested_enrollment",
  "math_#_tested",
  "math_not_tested_absent",
  "math_not_tested_refusal",
  "math_not_tested_scores_suppresed"
)
```

# 2016 data
```{r}
illinois_general_2017 <- read_excel("school_data/2017-Participation-Report-All-Districts.xlsx", skip = 4, col_names = FALSE)
```

2018-PARCC-SAT-Proficient

```{r}
excel_sheets("school_data/2018-PARCC-SAT-Proficient.xlsx")

```

